E Coli project paper

### 2013-07-15 paper/paper.tex

>>>>

The star shape (randst-96) Shows oscillations in nflD horizontally, two poles to two
poles.  There is sometimes a small amount of lag between the upper
maxima moving horizontally and the lower.  Half periods take roughly
25s. Dimensions are roughly 5.00 by 5.00?  Check this.

Randst (sort of triangle) is roughly dimensions of 3.5 by 3.5?
nflD oscillations appear to be half periods of 25s as well.  Maxima appear
at the poles and in the interim there are weak maxima in center pole.

Funny randst shape 98 shows nflD oscillations of about 30s or so.
